---
title: "data_import_test"
author: "Christian Stenbro"
date: "`r Sys.Date()`"
output: html_document
---

# 0. Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse,
               rjson,
               circular,
               rethinking, 
               widyr,
               ggthemes,
               betareg,
               lsa,
               sf,
               geosphere,
               extraDistr,
               bayesplot)
```

# 1. Loading data

```{r}
# change these to the correct paths if running on a different system

# loading Otree experiment data downloaded from the social cognition server
BTL_practice <- read_csv("/Users/christianstenbro/AU/BSc/data/BTL_practice_2025-01-06.csv")
BTL <- read_csv("/Users/christianstenbro/AU/BSc/data/BetweenTheLines_2025-01-06.csv")

# loading the demographic data downloaded from Prolific
prolific <- read_csv("/Users/christianstenbro/AU/BSc/data/prolific_export_06_01_2025_671fc245c729e00b501ead56.csv")

# loading the .csv file created with the sample creation script, containing geographic data
prolific_geography <- read_csv("/Users/christianstenbro/AU/BSc/data/prolific_sample_quotas_v3.csv")
```

# 2. Understanding the data structure

```{r}
# filtering the relevant participant labels in the practice round:
BTL_practice <- BTL_practice %>% filter(participant.label != "NA")

# the participant label is also in this one - fantastic!
BTL <- BTL %>% filter(participant.label != "NA")

# filtering for session
colnames(BTL)
all_participants <- unique(BTL$participant.label)
all_participants[200]
```


The data is organised by sessions and rounds. This means that sessions 1 will contain data for each individual participant for each consecutive round. But we can always just sort by participant:

```{r}
# loading data for one particular participant
BTL_participant_4 <- BTL %>% 
  arrange(participant.label) %>% 
  filter(participant.label == "5df1a3387caa1e0c69dca179")

# playing around with the data format
fromJSON(BTL_participant_4$player.angleData[2])
fromJSON(BTL_participant_4$player.startPosData[2])

# looking at the image
BTL_participant_4$player.drawing[6]
```

```{r}
# loading practice data from that participant
BTL_practice_participant <- BTL_practice %>% 
  arrange(participant.label) %>% 
  filter(participant.label == "5df1a3387caa1e0c69dca179")

# playing around with the data format
angle <- fromJSON(BTL_practice_participant$player.angleData[1])
fromJSON(BTL_practice_participant$player.startPosData[1])

# looking at the image
BTL_practice_participant$player.drawing[1]
```

# 3. Converting line angle data to radians

In order to plot the raw angle data, it is first converted to radians. Currently, it has a radian-like format, but instead of the range from 0 to 2π, it ranges from -π to π. Additionally, unlike radians that conventionally increase in the counter clockwise direction, starting from 0 at the horizontal line and ending at 2π, the current angle format increases clockwise. Thus the following transformations are made:

1. The signs of all data point are flipped (by multiplying with -1). This means that the angles on the upper half of the 'clock' will now correspond to their radian value.

2. For data points x where x < 0, the sign of x is flipped once again and the result is subtracted from 2π. This transforms the angle to the radian space.

```{r}
# flipping all signs

flipped_angles <- list()

for (i in 1:length(angle)){
  flipped_angles[i] <- angle[[i]] * -1
}

# transforming negative angles to radian space
radians <- list()

for (i in 1:length(flipped_angles)){
  if (flipped_angles[[i]] < 0){
    radians[i] <- (2 * pi) - (flipped_angles[[i]] * -1)
  }
  else {
    radians[i] <- flipped_angles[[i]]
  }
}

radians <- unlist(radians)
```

```{r}
# the data can now be plotted using tools from the circular package in R

# converting the data to circular data
radians <- as.circular( radians, units="radians", zero = 0, rotation = c("counter", "clock") )

# plotting the angles on a circle
plot(radians, stack=TRUE, bins=150) 

# Shrink the plot so that all points fit.
#plot(radians, stack=TRUE, bins=150, shrink=1.5) 

# Recentering the figure in a different place
#plot(radians, stack=TRUE, bins=150, xlim=c(-1,1.2), ylim=c(-1,0)) 

```

This achieves a different representation of the angles of each line for a given participant in a given round.

Let's try to expand this to all lines in the practice rounds:

```{r}
# removing data points for participants that did not reach the goodbye page
BTL_practice_cleaned <- BTL_practice %>% filter(participant._current_page_name == "Goodbye")

# selecting the relevant columns
BTL_practice_angles <- BTL_practice_cleaned %>% select(participant.label, player.angleData)

# doing sanity checks
nrow(BTL_practice_angles)
length(unique(BTL_practice_angles$participant.label))
```

First, a list of all angles unpacked from their respective nesting is computed:

```{r}
raw_angles <- list()

for ( i in 1:nrow(BTL_practice_angles) ){
  raw_angles[i] <- list( fromJSON( BTL_practice_angles$player.angleData[[i]] ) )
  
}

raw_angles <- unlist(unname(unlist(unname(raw_angles))))
```

Then, the angles are transposed to radians using a similar method as previously:

```{r}
# flipping all signs

flipped_angles <- list()

for (i in 1:length(raw_angles)){
  flipped_angles[i] <- raw_angles[[i]] * -1
}

# transforming negative angles to radian space
radians <- list()

for (i in 1:length(flipped_angles)){
  if (flipped_angles[[i]] < 0){
    radians[i] <- (2 * pi) - (flipped_angles[[i]] * -1)
  }
  else {
    radians[i] <- flipped_angles[[i]]
  }
}

radians <- unlist(radians)
```

The radians are plotted:

```{r}
# converting the data to circular data
radians <- as.circular( radians, units="radians", zero = 0, rotation = c("counter", "clock") )

# plotting
plot(radians, stack=TRUE, bins=360*10, shrink=1.5, 
     cex = 0.5, col=col.alpha( rangi2,0.05 ), 
     main = "Angle data from practice rounds, converted to radians",
     cex.main = 2) 

# could be cool to plot the density as well
dens(as.numeric(radians))

# The distribution is, essentially, bimodal; this is somewhat obscured by the density plot, which shows the peak around 0 and 2pi as two distinct peak, when they are really one!
```

If this is not due to some kind of mistake, the visualization shows very distinct peaks at angles corresponding to the Cartesian axes. Specifically large peaks are around r = 0 and r = 3π/2, corresponding to a horizontal line drawn from left to right; and a vertical line drawn from top to bottom.

```{r}
# 1 degree precision treshold in radians
precision_treshold <- 1/360*2*pi

is_angle_zero <- as.numeric(radians) <= precision_treshold

is_angle_zero <- tibble(is_angle_zero)

is_angle_zero %>% filter(is_angle_zero == TRUE)
```

1 degree = 1 * pi/180 * radians

# 4 Computing features

## 4.1 Pre-processing - creating angle matrix

Removing rows from internal testing:

```{r}
# selecting the relevant columns
BTL_angles <- BTL %>% select(participant.label, player.angleData, participant._current_page_name)

# grouping by participant label
BTL_angles <- BTL_angles %>% group_by(participant.label)

# removing data from internal tests of the experimental platform
test_labels <- c("pilot_a", "pilot_b", "pilot_c", "pilot_d", "test_1", "test_2", "test_3", "test_4")
BTL_angles <- BTL_angles %>% filter(!(participant.label %in% test_labels))

# removing data points for participants that did not reach the goodbye page
BTL_angles <- BTL_angles %>% filter(participant._current_page_name == "Goodbye")

# removing the current_page_name column 
BTL_angles <- BTL_angles %>% select(-participant._current_page_name)
```

```{r}
# checking the size of this sample

n_distinct(BTL_angles$participant.label)
```


Plotting the data:

```{r}
raw_angles <- list()

for ( i in 1:nrow(BTL_angles) ){
  raw_angles[i] <- list( fromJSON( BTL_angles$player.angleData[[i]] ) )
}

raw_angles <- unlist(unname(unlist(unname(raw_angles))))
```

Then, the angles are transposed to radians using a similar method as previously:

```{r}
# flipping all signs

flipped_angles <- list()

for (i in 1:length(raw_angles)){
  flipped_angles[i] <- raw_angles[[i]] * -1
}

# transforming negative angles to radian space
radians <- list()

for (i in 1:length(flipped_angles)){
  if (flipped_angles[[i]] < 0){
    radians[i] <- (2 * pi) - (flipped_angles[[i]] * -1)
  }
  else {
    radians[i] <- flipped_angles[[i]]
  }
}

radians <- unlist(radians)
```

The radians are plotted:

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/"
file_name = paste0(path_name, "all_angles.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# converting the data to circular data
radians <- as.circular( radians, units="radians", zero = 0, rotation = c("counter", "clock") )

# plotting
plot(radians, stack=TRUE, bins=360*100, shrink=1.8, 
     cex = 0.5, col=col.alpha( "blue",0.05 ), 
     main = "Angle data from all rounds",
     cex.main = 2, axes = FALSE) 

suppressWarnings(
  axis.circular(at = c(0, pi/2, pi, 3*pi/2), 
                labels = c("0°", "90°", "180°", "270°"), 
                tick = FALSE, cex = 0.5, tcl.text = 0.2)
  )

dev.off()

# could be cool to plot the density as well
dens(as.numeric(radians))

# This distribution is a bit more complex; hardly bimodal anymore. Instead, there are clear local peaks at all cardinal points + the midpoints between these.

# We can notice that a large chunk of the distribution is centered around zero or 2pi. This can create problems for the analysis later.
```
For a simpler overview, they can be plotted as a density curve estimate:

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/"
file_name = paste0(path_name, "kernel_dens_all_angles.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# estimating circle density
density_data <- density.circular(radians, bw = 20*20)

# plotting the density on a circle
par(mar = c(2, 2, 2, 2))

plot(density_data, col = "black", 
     lwd = 1, ylim = c(-2,1.5), xlim = c(-2,2),
     axes = FALSE, main = "Kernel density estimation for all data points", 
     ylab = "", cex = 0.2, shrink = 1.2)

# adding axis ticks and labels
suppressWarnings(
  axis.circular(at = c(0, pi/2, pi, 3*pi/2), 
                labels = c("0°", "90°", "180°", "270°"), 
                tick = TRUE, cex = 0.6, tcl.text = 0.2)
  )

dev.off()
```

To facilitate the analysis, it is necessary to restructure the data frame in the following way:

First, the data is arranged by participant label This creates a clear data structure with 6 succeeding rows for each participant:

```{r}
# arranging data by participant label
BTL_angles <- BTL_angles %>% arrange(by_group = participant.label)
```

The angle data for each row has to be unpacked from the JSON format recorded in Otree:

```{r}
# unpacking JSON data into a nested list format
raw_angles <- list()

for ( i in 1:nrow(BTL_angles) ){
  raw_angles[i] <- list( fromJSON( BTL_angles$player.angleData[[i]] ) )
}
```

There are many different options when it comes to restructuring the raw angle data.

For this mock-up analysis, I will make a data frame in long format where each participant figures 6 times. 

There will be 6 line variables, indicating the angle of each line for the round *i* in *i:6*. This necessarily means that there will be *NAs* or *0s* where no lines are present. I will have to think about whether this becomes a problem for the regression analysis later on. 

Trying to compose a data frame in long format manually, to look like the following:

Participant | LC 1 | LC 2 | LC 3 | . . . | LC 6 |
P_n         | {...}| {...}| {...}| . . . | {...}|

```{r}
# adding a line count variable to keep track of things
line_count <- rep(seq(1,6, by=1), nrow(BTL_angles)/6)
BTL_angles$line_count <- line_count

# adding empty columns for each possible line
BTL_angles <- BTL_angles %>% mutate(l1 = NA, l2 = NA, l3 = NA, l4 = NA, l5 = NA, l6 = NA)

# creating empty matrix
angle_matrix <- BTL_angles %>% ungroup %>% select(l1, l2, l3, l4, l5, l6, participant.label, line_count)

# defining n_distinct participants
unique_participants = n_distinct(BTL_angles$participant.label)

# unpacking the angle data into a data frame structure
for ( participant in seq(1:unique_participants) ) {

  for ( round_number in 1:6 ) {
    
    for ( line_number in seq(1:round_number) ) {
      
      matrix_row_index <- round_number + ( 6 * ( participant - 1 ) )
      matrix_column_index <- line_number
      
      angle_outer_index <- round_number + ( 6 * ( participant - 1) )
      angle_inner_index <- line_number
      
      named_angle <- raw_angles[[angle_outer_index]][angle_inner_index]
      
      angle_matrix[matrix_row_index, matrix_column_index] <- unname(unlist(named_angle))
    }
  }
}

# reordering the data frame
angle_matrix <- angle_matrix %>% select(participant.label, line_count, l1, l2, l3, l4, l5, l6)
```

And the angles are converted into radians, following the algorithm described in section 3:

*1. The signs of all data point are flipped (by multiplying with -1). This means that the angles on the upper half of the 'clock' will now correspond to their radian value.*

*2. For data points x where x < 0, the sign of x is flipped once again and the result is subtracted from 2π. This transforms the angle to the radian space.*

```{r}
angle_columns <- c("l1", "l2", "l3", "l4", "l5", "l6")

# flipping the sign of all data points
radian_matrix <- angle_matrix %>% mutate( across( c(l1:l6), ~ .*-1 ) )

# for data points x where x < 0, the sign of x is flipped once again and the result is subtracted from 2π. This transforms the angle to the radian space.
radian_matrix <- radian_matrix %>% mutate( across( c(l1:l6), ~ case_when(
  . < 0 ~ (2 * pi) - (. * -1),
  TRUE ~ . # leaves positive values unchanged
)))

# assessing the final data structure
head(radian_matrix)
```


## 4.2 Computing number of intersections

Somewhat discouraged by the difficulty of modelling the raw angles, I will continue on to the second model: Modelling the number of intersections as a function of round_number that interacts with the distance matrix.

This model requires the following steps:

1. Compute line intersections

2. Merge the line data with the demographic data from prolific

3. Construct a distance matrix

4. Fit a model 

Before fitting the model, we should think about the nature of the outcome variable. In this case, fitting the data as a conditional poisson distribution could make sense, as we are dealing with positive integers.

### 4.2.0 Preprocessing

Extracting the line starting position data

```{r}
# selecting the relevant columns
BTL_lines <- BTL %>% select(participant.label, player.startPosData, participant._current_page_name)

# grouping by participant label
BTL_lines <- BTL_lines %>% group_by(participant.label)

# removing data from internal tests of the experimental platform
test_labels <- c("pilot_a", "pilot_b", "pilot_c", "pilot_d", "test_1", "test_2", "test_3", "test_4")
BTL_lines <- BTL_lines %>% filter(!(participant.label %in% test_labels))

# removing data points for participants that did not reach the goodbye page
BTL_lines <- BTL_lines %>% filter(participant._current_page_name == "Goodbye")

# removing the current_page_name column 
BTL_lines <- BTL_lines %>% select(-participant._current_page_name)
```

```{r}
# arranging data by participant label
BTL_lines <- BTL_lines %>% arrange(by_group = participant.label)
```

The line starting position data for each row has to be unpacked from the JSON format recorded in Otree:

```{r}
# unpacking JSON data into a nested list format
raw_lines <- list()

for ( i in 1:nrow(BTL_lines) ){
  raw_lines[i] <- list( fromJSON( BTL_lines$player.startPosData[[i]] ) )
}
```

An extra complication here is that each line has two data points (coordinates) associated with it!

```{r}
# adding a line count variable to keep track of things
line_count <- rep(seq(1,6, by=1), nrow(BTL_lines)/6)
BTL_lines$line_count <- line_count

# adding empty columns for each possible line
BTL_lines <- BTL_lines %>% mutate(l1_x = NA, l1_y = NA,
                                  l2_x = NA, l2_y = NA,
                                  l3_x = NA, l3_y = NA, 
                                  l4_x = NA, l4_y = NA,
                                  l5_x = NA, l5_y = NA,
                                  l6_x = NA, l6_y = NA)

# creating empty matrix
line_matrix <- BTL_lines %>% ungroup %>% select(c(l1_x:l6_y), participant.label, line_count)

# defining n_distinct participants
unique_participants = n_distinct(BTL_lines$participant.label)

# unpacking the line data into a data frame structure
for ( participant in seq(1:unique_participants) ) {

  for ( round_number in 1:6 ) {
    
    for ( line_number in seq(1:round_number) ) {
      
      for ( coordinate in 1:2 ) {
      
        matrix_row_index <- round_number + ( 6 * ( participant - 1 ) )
        matrix_column_index <- line_number
      
        line_outer_index <- round_number + ( 6 * ( participant - 1) )
        line_inner_index <- line_number
      
        named_line <- raw_lines[[line_outer_index]][[line_inner_index]][coordinate]
      
        if (coordinate == 1) {
          # adding the x coordinate
          line_matrix[matrix_row_index, (matrix_column_index*2)-1] <- unname(unlist(named_line))
        } else {
          # adding the y coordinate
          line_matrix[matrix_row_index, matrix_column_index*2] <- unname(unlist(named_line))
        }
      }
    }
  }
}

# reordering the data frame
line_matrix <- line_matrix %>% select(participant.label, line_count, l1_x:l6_y)

# assessing the data frame
line_matrix
```

This looks right! Now we can proceed to merging this with the angle data:

```{r}
line_angle_data <- merge(angle_matrix, line_matrix, by = c("participant.label", "line_count"))
```

```{r}
range(angle_matrix$l1)
```


This data frame now contains angle and starting position information for each line in each drawing by each participant.

### 4.2.1 Computing line intersections

Before doing any computations, the data is transformed into a long format with the following structure:

round | line_nr | angle | x_1 | y_1 | x_2 | y_2 | . . .

1     | 1       | 𝜃    | i   | j   | k   | l   |
2     | 1       | 𝜃    | i   | j   | k   | l   |
2     | 2       | 𝜃    | i   | j   | k   | l   |
3     | 1       | 𝜃    | i   | j   | k   | l   |
3     | 2       | 𝜃    | i   | j   | k   | l   |
3     | 3       | 𝜃    | i   | j   | k   | l   |
.
.
.

This would also be good to get rid of the NAs.

```{r}
# Trying to transform the data into a long format

# transforming angles, x- and y-coordinates separately 
angles_long <- line_angle_data %>% pivot_longer(
    cols = l1:l6, 
    names_to = "angle_index",
    values_to = "angle",
    values_drop_na = TRUE) %>% mutate(row_id = row_number()) %>% 
  select(-c(l1_x:l6_y))

x_long <- line_angle_data %>% pivot_longer(
    cols = c(l1_x, l2_x, l3_x, l4_x, l5_x, l6_x), 
    names_to = "x_1_index",
    values_to = "x_1",
    values_drop_na = TRUE) %>% mutate(row_id = row_number()) %>% 
  select(-c(l1:l6_y))

y_long <- line_angle_data %>% pivot_longer(
    cols = c(l1_y, l2_y, l3_y, l4_y, l5_y, l6_y), 
    names_to = "y_1_index",
    values_to = "y_1",
    values_drop_na = TRUE) %>% mutate(row_id = row_number()) %>% 
  select(-c(l1:l6_x))

# merging the 3 transformed data frames
data_long <- merge(angles_long, x_long, by = "row_id")
data_long <- merge(data_long, y_long, by = "row_id")

# checking that the merging has gone correctly
identical(data_long$line_count.x, data_long$line_count.y)
identical(data_long$line_count.x, data_long$line_count)
identical(data_long$line_count, data_long$line_count.y)

# removing redundant rows
data_long <- data_long %>% select(-c(line_count.x,line_count.y), 
                                  -c(x_1_index, y_1_index, angle_index),
                                  -c(participant.label.x, participant.label.y),
                                  -row_id)
# changing the order of columns
data_long <- data_long %>% select(participant.label, line_count, angle, x_1, y_1)

# checking the logic of the dimensions of the long data frame
obs_pr_participant <- data_long %>% filter(participant.label == participant.label[1]) %>% n_distinct()
obs_in_total = obs_pr_participant * n_distinct(data_long$participant.label)
nrow(data_long) == obs_in_total

# assessing the transformed data
head(data_long)
```
Also, the y-coordinates have been recorded in a matrix fashion, meaning that y = 0 corresponds to the top of the canvas and y = 400 to the bottom. 

I will flip the y coordinates to make it easier to compute and visualise the line intersections:

```{r}
# changing the range of the y coordinates
data_long <- data_long %>% mutate(y_1 = 400 - y_1)

# displaying the new range
range(data_long$y_1)
```

Now it's time to compute intersections. 
First, to get an overview of the available information:

For each line, we have:

  - an origin point *OP(x_1, y_1)*,
  - an angle relative to the horizon *𝜃*, 
  - and a fixed line length *r* of 215 units. 

We can now find the endpoint *EP(x_2, y_2)* relative to the starting point using the following properties:

$$\cos(\theta) = \frac{\Delta_x}{r}$$
$$\Delta_x=\cos(\theta)\cdot r$$
and:

$$\sin(\theta)=\frac{\Delta_y}{r}$$
$$\Delta_y = -\sin(\theta)\cdot r$$
Note that sin(𝜃)·r has to be negative due to the earlier reversal of the y-axis.

The final coordinates are obtained by addition with the starting point:
$$  \begin{bmatrix} x_2 \\ y_2 \end{bmatrix} = \begin{bmatrix} x_1 + \Delta_x \\ y_1 + \Delta_y \end{bmatrix}$$ 

The long data frame should be a good starting point for computing a new column with x and y coordinates for the ending points:

```{r}
# extracting a drawing to make sure the coordinates fit
drawings <- BTL %>% filter(participant.label == "66c6121bc818a545e0d5ca0d") %>% select(player.drawing)
drawings[[1]][2]

drawings
```

```{r}
# defining the line length
r = 215

# creating new columns that contain end points for the lines
data_long <- data_long %>% mutate(x_2 = x_1 + cos(angle)*r,
                                  y_2 = y_1 + -sin(angle)*r)
```

```{r}
# setting seed
set.seed(2024)

# defining the number of participants and creating a vector of participant ids
participant_n = n_distinct(data_long$participant.label)
participant_ids <- unique(data_long$participant.label)

# sampling a single drawing
line_drawing <- data_long %>% filter(line_count==2 & participant.label==participant_ids[sample(participant_n, 1)])

# we now have a drawing with four lines
line_drawing
```

First, I will test if the 'sf' library can be used to find intersections

```{r}
# creating lines as simple feature objects
l1_x1 <- line_drawing$x_1[1]
l1_y1 <- line_drawing$y_1[1]

l1_x2 <- line_drawing$x_2[1]
l1_y2 <- line_drawing$y_2[1]

l2_x1 <- line_drawing$x_1[2]
l2_y1 <- line_drawing$y_1[2]

l2_x2 <- line_drawing$x_2[2]
l2_y2 <- line_drawing$y_2[2]

line_1 <- st_linestring(rbind(c( l1_x1 , l1_y1 ), c( l1_x2 , l1_y2 )))
line_2 <- st_linestring(rbind(c( l2_x1 , l2_y1 ), c( l2_x2 , l2_y2 )))

# collecting lines in a new object
lines <- st_sf(geometry = st_sfc(line_1, line_2))

# computing intersection
intersection <- st_intersection(line_1, line_2)

# plotting the lines
plot(line_1, col = "blue", lwd = 2, main = "2 line drawing from participant 66c6121bc818a545e0d5ca0d")
plot(line_2, col = "red", lwd = 2, add = TRUE)

# plotting the intersection if it exists
if (!st_is_empty(intersection)) {
  intersection_coords <- st_coordinates(intersection)
  points(intersection_coords[,1], intersection_coords[,2],col = "black", pch = 19, cex = 1.5)
  legend("topright", legend = "Intersection", col = "black", pch = 19, cex = 0.8)
}
```
This is great, because it works!

The next steps are to: 

- Generalize the above steps so that it can find and plot intersections for drawings with up to six lines
  [Comment: I should test whether the intersection function can deal with more than 2 lines at the same time . . .]

- Return (a) the number of sections for a given drawing and (b) the intersection points [perhaps not useful?]?

- Compute alphas and betas (in the parametric line representations) and store them somewhere

First, I will try the same thing but this time with 3 lines

```{r}
# setting seed
set.seed(2024)

# defining the number of participants and creating a vector of participant ids
participant_n = n_distinct(data_long$participant.label)
participant_ids <- unique(data_long$participant.label)

# sampling a single drawing
three_line_drawing <- data_long %>% filter(line_count==3 & participant.label==participant_ids[sample(participant_n, 1)])

# we now have a drawing with four lines
three_line_drawing
```

```{r}
# creating lines as simple feature objects
l1_x1 <- three_line_drawing$x_1[1]
l1_y1 <- three_line_drawing$y_1[1]

l1_x2 <- three_line_drawing$x_2[1]
l1_y2 <- three_line_drawing$y_2[1]

l2_x1 <- three_line_drawing$x_1[2]
l2_y1 <- three_line_drawing$y_1[2]

l2_x2 <- three_line_drawing$x_2[2]
l2_y2 <- three_line_drawing$y_2[2]

l3_x1 <- three_line_drawing$x_1[3]
l3_y1 <- three_line_drawing$y_1[3]

l3_x2 <- three_line_drawing$x_2[3]
l3_y2 <- three_line_drawing$y_2[3]

line_1 <- st_linestring(rbind(c( l1_x1 , l1_y1 ), c( l1_x2 , l1_y2 )))
line_2 <- st_linestring(rbind(c( l2_x1 , l2_y1 ), c( l2_x2 , l2_y2 )))
line_3 <- st_linestring(rbind(c( l3_x1 , l3_y1 ), c( l3_x2 , l3_y2 )))

# collecting lines in a new object
lines_sf <- st_sf(geometry = st_sfc(
  line_1, 
  line_2, 
  line_3
  ))

# computing intersection
intersections <- st_intersection(lines_sf)

# getting the points out
point_intersections <- intersections[st_geometry_type(intersections) == "POINT", ]

# plotting the lines
plot(lines_sf$geometry, col = "blue", lwd = 2, main = "3 line drawing from participant 66c6121bc818a545e0d5ca0d")

# plotting the intersection if it exists
if (nrow(point_intersections) > 0) {
  intersection_coords <- st_coordinates(point_intersections)
  points(intersection_coords[,1], intersection_coords[,2],col = "black", pch = 19, cex = 1.5)
  legend("topright", legend = "Intersection(s)", col = "black", pch = 19, cex = 0.8)
}

#st_coordinates(point_intersections)
#st_coordinates(test1[2]$intersection_points)
```
Trying to make the same as the above but this time generalized

```{r}
# defining function to check line intersections
find_intersections <- function(drawing) {
  
  # extract line count
  line_count <- unique(drawing$line_count) 
  
  # set up an empty list
  line_list <- list()
  
  # creating an sf object
  for (i in 1:line_count) {
    
    # extract line coordinates for each line
    line <- st_linestring(rbind(c( drawing$x_1[i] , drawing$y_1[i] ), 
                                    c( drawing$x_2[i] , drawing$y_2[i] )))
    
    # add the lines to the list
    line_list[[i]] <- line
  }
  
  # create an sf object from the line list  
  lines_sf <- st_sf(st_sfc(line_list))
  
  # compute intersections
  intersections <- st_intersection(lines_sf)
  
  intersection_points <- intersections[st_geometry_type(intersections) == "POINT", ]
  
  # return both the lines and the intersections
  return(list(lines_sf = lines_sf, 
              intersection_points = intersection_points,
              intersection_count = nrow(intersection_points)))
}

# testing the function
test1 <- find_intersections(three_line_drawing)

# plotting the lines
plot(st_geometry(test1[1]$lines_sf), col = "blue", lwd = 2)

# plotting the intersection if it exists
if (nrow(test1[2]$intersection_points) > 0) {
  intersection_coords <- st_coordinates(test1[2]$intersection_points)
  points(intersection_coords[,1], intersection_coords[,2],col = "black", pch = 19, cex = 1.5)
  legend("topright", legend = "Intersection(s)", col = "black", pch = 19, cex = 0.8)
}
```
For the next iteration, the function is generalised to take any drawing

```{r}
# plot n random drawings with intersections
for (i in 1:10){

  # defining the number of participants and creating a vector of participant ids
  participant_n = n_distinct(data_long$participant.label)
  participant_ids <- unique(data_long$participant.label)
  
  # sampling a single drawing
  drawing <- data_long %>% 
    filter(line_count==sample(1:6,1) & participant.label==participant_ids[sample(participant_n, 1)])
  
  # trying out the function
  test2 <- find_intersections(drawing)
  
  # plotting the lines
  plot(st_geometry(test2[1]$lines_sf), col = "blue", lwd = 2,
       main = paste(unique(drawing$line_count), "line drawing by participant",
                    unique(drawing$participant.label))
       )
  
  #plotting the intersection if it exists
  if (nrow(test2[2]$intersection_points) > 0) {
    intersection_coords <- st_coordinates(test2[2]$intersection_points)
    points(intersection_coords[,1], intersection_coords[,2],col = "black", pch = 19, cex = 1.5)
    legend("topright", legend = "Intersection(s)", col = "black", pch = 19, cex = 0.8)
    }

print(unique(drawing$participant.label))

}
```

```{r}
# extracting drawing to test the issue of missing line width currently
drawings <- BTL %>% filter(participant.label == "65fb1bd8a35ac2c5ea01db6c") %>% select(player.drawing)
drawings[[1]][6]

# realising that the drawings are flipped . . . 
```

Currently, the *find_intersections* function takes a drawing (all 'lines' [rows] associated with the same round for the same participants) and computes the number of intersections for that drawing. 

To construct a feature column with intersections, I will construct a simple for loop. One thing to keep in mind is that the single line drawings will all contain 0 intersections. I will keep them in for now, but they should be filtered out later for the analysis.


```{r}
# creating vector of participant IDs and storing the length of this vector
participant_ids <- unique(data_long$participant.label)
participant_n = n_distinct(data_long$participant.label)

# setting up the empty variables
participant.label <- list()
line_count <- list()
intersection_count <- list()

# creating a loop
for (participant in 1:length(participant_ids)) {
  
  for (round in 1:6) {
    
    # creating a subset of lines for each round for each participant
    participant_subset <- data_long %>% filter(participant.label == participant_ids[participant]) %>% filter(line_count == round)
    
    # computing the line intersections
    line_intersections <- find_intersections(drawing = participant_subset)
    
    # storing information  
    participant.label[ 6 * (participant-1) + round] <- unique(participant_subset$participant.label)
    
    line_count[ 6 * (participant-1) + round] <- unique(participant_subset$line_count)
      
    intersection_count[ 6 * (participant-1) + round] <- line_intersections$intersection_count
  
  }
}

# combining the lists into a data frame
intersection_data <- data_frame(participant.label = unlist(participant.label),
                                line_count = unlist(line_count),
                                intersection_count = unlist(intersection_count))

# inspecting the data frame
head(intersection_data)
```

```{r}
# testing that everything adds up by looping through a number of drawings, plotting them with intersections, and displaying the intersection count information from the new intersection_data data frame
for (i in 1:20) {

  drawing <- data_long %>% 
    filter(line_count==intersection_data$line_count[i] & participant.label==intersection_data$participant.label[i])
    
  test3 <- find_intersections(drawing)
    
  # plotting the lines
  plot(st_geometry(test3[1]$lines_sf), col = "blue", lwd = 2,
       main = paste(unique(drawing$line_count), "line drawing by participant", unique(drawing$participant.label)),
       sub = paste("intersection count = ", intersection_data$intersection_count[i])
       )
    
  #plotting the intersection if it exists
  if (nrow(test3[2]$intersection_points) > 0) {
      intersection_coords <- st_coordinates(test3[2]$intersection_points)
      points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 1.5)
      legend("topright", legend = "Intersection(s)", col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 0.8)
  }
}
```
Comments: 

The intersection count reflects the number of intersections computed for each drawing.
The main issue with the current implementation of intersection count, is that some lines can be very close without actually intersections.

A relevant questions here is whether it would be better to extend the line so they mimic the thickness of the lines used in the drawing program. This would mitigate the problem of a small mismatch between intersections in the drawing platform being deemed non-intersections in the analysis. 

However, it would not fix the problem of what could be considered *a likely intention of intersection* on the part of the participant; where the goal appears to be the creation (or suggestion) of a closed form, but the lines do not exactly meet. 

For example, many of the 'squares' in the above sample looks to be having this issue as the intersections are happening very close to the ends of the lines.

```{r}
drawings <- BTL %>% filter(participant.label == "5773ac203146cb0001d1a27b") %>% select(player.drawing)
drawings[[1]][2]
```

I will not try to solve these issues, but will report on them as limitations to the current mode of analysis.

### 4.2.2 Merging the intersection data frame with demographic and geographic data

```{r}
# checking the raw distribution of intersections with an without 0 included
par(mfrow=c(1, 2))

simplehist(intersection_data$intersection_count,
           xlab = "intersections",
           main = paste("n = ", length(intersection_data$intersection_count)))

simplehist(intersection_data$intersection_count[intersection_count != 0],
           xlab = "intersections",
           main = paste("n = ", length(intersection_data$intersection_count[intersection_count != 0])))
```

```{r}
# inspecting the prolific data frame
head(prolific)
```
Selecting relevant columns and getting and overview of the sample:

```{r}
# filtering out rows for the participant who did not receive automatic approval
# and selecting the rows with the demographic data of interest to the analysis
demographic_data <- prolific %>% 
  filter(Status == "APPROVED") %>%
  select(participant.label = `Participant id`,
         country_of_birth = `Country of birth`,
         country_of_residence = `Country of residence`,
         nationality = Nationality,
         gender = Sex,
         age = Age)

# checking the gender distribution of the sample
gender_table <- table(demographic_data$gender)

barplot(gender_table, lwd = 2, col = c(3,7,6),
        main = "Declared gender distribution of the participant sample")

# checking the age distribution of the sample
demographic_data$age <- as.numeric(demographic_data$age)

simplehist(demographic_data$age, xlab = "age (years)", main = "Participant age distribution")

# checking the distribution by nationality
table(demographic_data$nationality)
```
The sample is fairly balanced in terms of male and female participants. 
The age distribution is skewed towards participants between 20 and 30. 

Since we have no reason to believe that either age, nor gender would affect the data in any particular way, we will simply note these qualities of the sample. But neither of the variables, gender and age, will be included the analyses.

Now, the data is merged with the intersection data frame:

```{r}
# merging data frames
intersection_prolific_merge <- merge(intersection_data, demographic_data, by = "participant.label")

# arranging the data according to participant id and line count
intersection_prolific_merge <- intersection_prolific_merge %>% group_by(participant.label) %>% arrange(by_group = participant.label, line_count)
```
The next step is to merge the newly combined data frame with the data frame from the sample creation process, containing geographic information (country centroids), that will be used to create a distance matrix:

```{r}
# checking that the country names match:
n1 <- sort(unique(prolific_geography$country_name))
n2 <- sort(unique(intersection_prolific_merge$nationality))
n1==n2
```

```{r}
colnames(prolific_geography)
```

```{r}
# merging the data
intersection_prolific_geography <- merge(intersection_prolific_merge, prolific_geography, 
                                         by.x = "nationality", by.y = "country_name")

# sorting the data according to participant and linecount
intersection_prolific_geography <- intersection_prolific_geography %>% 
  group_by(participant.label) %>% 
  arrange(by_group = participant.label, line_count)
```

Comment: Nationality is here used as the demographic basis for computing the distances.

```{r}
# checking the distribution by nationality
table(intersection_prolific_geography$macroarea_name)
```

## 4.3 Computing cosine similarity with a horizontal vector

### 4.3.1 Preparing data

First, I will prepare a data frame with the relevant information. Unlike the line intersection analysis where we need a single row for each drawing, the angle analysis requires a row pr. line. This is what we have in the original 'data_long' data frame created for an earlier step in the previous analysis.

```{r}
head(data_long)
```

I will merge this data frame with the data frames containing demographic and geographic information:

```{r}
# creating a subset from the prolific demographic data
demographic_data <- prolific %>%
  filter(Status == "APPROVED") %>%
  select(participant.label = `Participant id`,
         country_of_birth = `Country of birth`,
         country_of_residence = `Country of residence`,
         nationality = Nationality,
         gender = Sex,
         age = Age)
```

```{r}
# merging data frames
angle_prolific_merge <- merge(data_long, demographic_data, by = "participant.label", all.x = TRUE)

# arranging the data according to participant id and line count
angle_prolific_merge <- angle_prolific_merge %>% group_by(participant.label) %>% arrange(by_group = participant.label, line_count)

# finding missing matches
angle_prolific_merge %>% filter(is.na(country_of_birth)) %>% summarise(unique(participant.label))
```

Notice that in the current data downloads, 8 participants in the Otree experiment is not matched in the prolific data download. The data for these participants will have to be dropped from the analysis (which is done automatically using merge without the all.x = TRUE argument):

```{r}
# merging data frames
angle_prolific_merge <- merge(data_long, demographic_data, by = "participant.label")

# arranging the data according to participant id and line count
angle_prolific_merge <- angle_prolific_merge %>% group_by(participant.label) %>% arrange(by_group = participant.label, line_count)
```

```{r}
# merging the data with the geographic data frame
angle_prolific_geography <- merge(angle_prolific_merge, prolific_geography,
                                         by.x = "nationality", by.y = "country_name")

# sorting the data according to participant and linecount
angle_prolific_geography <- angle_prolific_geography %>%
  group_by(participant.label) %>%
  arrange(by_group = participant.label, line_count)
```

```{r}
# selecting and rearranging the columns needed for the analysis
angle_data <- angle_prolific_geography %>% select(participant.label,
                                                  line_count,
                                                  angle,
                                                  x_1, y_1, x_2, y_2,
                                                  nationality,
                                                  macroarea)
```

Notice: The angles in the long data frame are recorded in reversed radians from [-pi,pi] (this is how they were recorded in Otree). I will transform them to non-reversed radians, so that drawing a line from the top to the bottom of the canvas corresponds to a -pi/2 angle.

I will also add an extra macroarea variable coded as integers:

```{r}
# reversing angle range
angle_data <- angle_data %>% mutate(angle = angle * -1)

# coding integer macroarea variable
angle_data$macroarea <- as.factor(angle_data$macroarea)
angle_data$macroarea_int <- as.integer(angle_data$macroarea)

head(angle_data)
```

```{r}
# writing to csv
write_csv(angle_data, file = "/Users/christianstenbro/AU/BSc/data/angle_data.csv")
```

### 4.3.2 Computing feature

To compute the relative horizontality/verticality/obliquety of each line in each drawing, the all angles will be assigned a new value expressing their cosine similarity with a horizontal vector.

First, two new columns representing the cosine and sine of each angle are computed:

```{r}
angle_data <- angle_data %>% 
  mutate(cos = cos(angle),
         sin = sin(angle))
```

Then the cosine similarity between each line and a horizontal vector can now be computed. 

A horizontal vector forming an angle v between itself and the x-axis, corresponding to 0 degrees, is characterised by the following properties: cos(v) = 1, sin(v) = 0. 

```{r}
# implementing cosine similarity function
cosine_similarity <- function(vector_1, vector_2) {

  dot_product <- (vector_1[1] * vector_2[1]) + (vector_1[2] * vector_2[2])
  
  # Calculate the magnitudes of the vectors
  magnitude_1 <- sqrt(sum(vector_1^2))
  magnitude_2 <- sqrt(sum(vector_2^2))
  
  # Return the cosine similarity
  return(dot_product / (magnitude_1 * magnitude_2))
}

# testing the function
v1 <- c(0.8829342, -0.4694968)
v2 <- c(1,0)

cosine_similarity( v1 , v2 )

# comparing this with the lsa implementation
lsa::cosine(v1, v2) == cosine_similarity( v1 , v2 )
```

```{r}
# defining horizontal vector
h <- c(1,0)

# computing the absolute cosine similarity for each line
angle_data <- angle_data %>% 
  rowwise() %>% mutate(cosine_similarity_h = abs(cosine(c(cos, sin), h)))

# visualising the cosine similarities 
dens(angle_data$cosine_similarity_h)
```

```{r}
angle_data
```

Now, we can display this measure with random sets of individual drawings:

```{r}
for (i in 1:40) {

drawing <- angle_data %>% filter(participant.label == participant_ids[i], line_count == 5)
  
  test3 <- find_intersections(drawing)
  
  ID <- unique(drawing$participant.label)
    
  # plotting the lines
  plot(st_geometry(test3[1]$lines_sf), col = "blue", lwd = 2,
       main = paste(unique(drawing$line_count), "line drawing by participant",
                    unique(drawing$participant.label)),
       sub = paste("intersection count = ", test3$intersection_count,
                   "\n mean cosine similarity h = ", round(mean(drawing$cosine_similarity_h),3))
       )
    
  #plotting the intersection if it exists
  intersection_coords <- st_coordinates(test3[2]$intersection_points)
  
  points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), 
         pch = 19, cex = 1.5)
  
  legend("topright", legend = "Intersection(s)", col = col.alpha("orange", alpha = 0.8), 
         pch = 19, cex = 0.8)
  
}
```

```{r}
for (i in 1:20) {

drawing <- angle_data %>% filter(participant.label == participant_ids[i], line_count == 1)
  
  test3 <- find_intersections(drawing)
  
  ID <- unique(drawing$participant.label)
    
  # plotting the lines
  plot(st_geometry(test3[1]$lines_sf), col = "blue", lwd = 2,
       main = paste(unique(drawing$line_count), "line drawing by participant",
                    unique(drawing$participant.label)),
       sub = paste("\n mean cosine similarity h = ", round(mean(drawing$cosine_similarity_h),3))
       )
    
  #plotting the intersection if it exists
  intersection_coords <- st_coordinates(test3[2]$intersection_points)
  
  points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), 
         pch = 19, cex = 1.5)
  
}
```

The data is now aggregated to be ready for analysis:

```{r}
# aggregating data
angle_data_aggregated <- angle_data %>% group_by(participant.label, line_count) %>% 
  summarise(cosine_similarity_h = mean(cosine_similarity_h),
            participant.label = unique(participant.label),
            line_count = unique(line_count),
            macroarea = unique(macroarea)
  )
```

```{r}
# plotting the density distribution for each level of the line count variable
par(mfrow = c(2,3))
for (i in 1:6) {
  dens(angle_data_aggregated$cosine_similarity_h[angle_data_aggregated$line_count == i], 
       main = paste("line count = ", i))
  }
```

Comment: It is interesting to see the pronounced peak in the middle of the scale for line count = 4. This could be something to look into.

## 4.4 Computing the cosine similarity between lines

The first step is to compute an average cosine similarity for a single participant:

```{r}
# creating a data frame with angles (in their cos and sin expression) and transposing it
cos_sin_df = t(data_frame(cos = angle_data$cos[angle_data$participant.label == participant_ids[1]],
               sin = angle_data$sin[angle_data$participant.label == participant_ids[1]]))

# computing cosine similarities pairwise
cosine_similarities <- lsa::cosine(cos_sin_df)

# checking the dimensions of the cosine_similarities matrix - should be 21*21
dim(cosine_similarities)

# computing the average cosine_similarity
mean(cosine_similarities)
```

Since the matrix is symmetrical around the diagonal, which itself contain self-correlations for all lines in the drawing, the mean only has to be of one of the 'triangles' of the matrix, excluding the diagonal.

Note: It should be the absolute cosine similarity already at this level; if not, it will create errors, such as the square having a mean cosine similarity of 0, when the result should be around 0.5. We should not distinguish between lines that are drawn from different directions, yet appear visually similar.

```{r}
# creating a data frame with angles (in their cos and sin expression) and transposing it
for (i in 1:40) {

drawing <- angle_data %>% filter(participant.label == participant_ids[i], line_count == 2)

cos_sin_df = t(data_frame(cos = drawing$cos,
               sin = drawing$sin))

# computing cosine similarities pairwise
cosine_similarities <- lsa::cosine(cos_sin_df)

# checking the dimensions of the cosine_similarities matrix - should be 21*21
dim(cosine_similarities)

# computing the average cosine_similarity
total_mean <- mean(cosine_similarities)
lower_tri_mean <- mean(abs(cosine_similarities[lower.tri(cosine_similarities, diag = FALSE)]))

# plotting

  test3 <- find_intersections(drawing)
  
  ID <- unique(drawing$participant.label)
    
  # plotting the lines
  plot(st_geometry(test3[1]$lines_sf), col = "blue", lwd = 2,
       main = paste(unique(drawing$line_count), "line drawing by participant", unique(drawing$participant.label)),
       sub = paste("intersection count = ", test3$intersection_count,
                   "\nmean cosine similarity = ", round(total_mean, 3),
                   "\nabsolute of the lower triangle mean = ", round(lower_tri_mean, 3))
       )
    
  #plotting the intersection if it exists
      intersection_coords <- st_coordinates(test3[2]$intersection_points)
      points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 1.5)
      legend("topright", legend = "Intersection(s)", col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 0.8)
      
}
```

This can now be computed for all drawings:

```{r}
# computing the mean cosine similarity for each drawing
consine_similarity_drawing_level <- angle_data %>% 
  filter(line_count != 1 ) %>% 
  group_by(participant.label, line_count) %>%
  summarize(cosine_similarity_mean = {
      cos_sin_matrix <- t(data.frame(cos = cos, sin = sin))
  
      cosine_similarities <- lsa::cosine(cos_sin_matrix)
      
      abs(mean(cosine_similarities[lower.tri(cosine_similarities, diag = FALSE)]))
    },
  ) %>% 
  ungroup()

# adding a rounded mean column
consine_similarity_drawing_level <- consine_similarity_drawing_level %>% mutate(rounded_mean = round(cosine_similarity_mean, 3))

# plotting some subsets
par(mfrow=c(2,3))

for (i in 2:6) {
  sub <- consine_similarity_drawing_level %>% filter(line_count == i) %>% select(cosine_similarity_mean) 
  dens(sub$cosine_similarity_mean)
  title(main = paste(i, " lines"), cex.main = 0.8, line = 0.3)
}
mtext("Between line cosine similarity for different line counts", outer = TRUE, cex = 1, line = -2)
```
The plot shows a clear tendency for parallel lines for lower counts, with more angular diversity at higher levels. This is quite interesting!

Before the analysis, I will append the geographic data to the cosine similarity data frame:

```{r}
# extracting geographic data from the angle data frame
angle_geographic_subset_2 <- angle_data %>% 
  filter(line_count != 0) %>% 
  group_by(participant.label, line_count) %>% 
  summarise(participant.label = unique(participant.label),
            line_count = unique(line_count),
            macroarea = unique(macroarea),
            macroarea_int = unique(macroarea_int))

# merging the data frame with the cosine similarity data
cs_data <- merge(consine_similarity_drawing_level, angle_geographic_subset_2, by = c("participant.label","line_count"))

# inspecting the merged data frame
cs_data
```

Comment: Since the 1-line drawings can't have any between line similarity, this data frame is shorter compared to those containing the other features. This means that there will be NAs when merging the data frames.

## 4.5 Merging features

A single data frame with all features is created:

```{r}
# selecting features
f1 <- angle_data_aggregated

f2 <- intersection_prolific_merge %>% select(participant.label, line_count, intersection_count)

f3 <- cs_data %>% select(participant.label, line_count, abs_avg_between_line_cosine_sim = cosine_similarity_mean)

# merging features
feature_data_set <- merge(f1, f2, by = c("participant.label", "line_count"))

feature_data_set <- merge(feature_data_set, f3, all.x = TRUE, by = c("participant.label", "line_count")) # creates NAs for line_count 1

head(feature_data_set)
```

# 5 Different visualisations

## 5.1 Plotting density estimates of angle distribution for different regions and line counts

```{r}
# creating a macroarea name index
macroarea_idx <- unique(angle_data$macroarea)

# renaming papunesia to multinesia
#levels(macroarea_idx)[levels(macroarea_idx) == "Papunesia"] <- "Multinesia"
```

```{r}
# setting up a plot grid
par(mfrow = c(2,3))

# plotting the density estimate for all angles for all macroareas
for (i in 1:6){
  
  angle_set <- angle_data %>% filter(macroarea == macroarea_idx[i]) %>% select(angle)

  angle_set <- as.circular( angle_set$angle, types = "angle", 
                            template = "none", modulo = "asis", 
                            units="radians", zero = 0, 
                            rotation = c("counter", "clock") )
         
  # estimating circle density
  density_data <- density.circular(angle_set, bw = 20*5)
  
  # plotting the density on a circle
  par(mar = c(2, 2, 2, 2))
  
  plot(density_data, col = "black", 
       lwd = 1, ylim = c(-2,1.5), xlim = c(-1,3),
       axes = FALSE, main = "",
       cex.main = 0.7, ylab = "")
  title(main = paste(macroarea_idx[i]), adj = 0.1)
  
  # adding axis ticks and labels
  suppressWarnings(
    axis.circular(at = c(0, pi/2, pi, 3*pi/2), 
                  labels = c("0°", "90°", "180°", "270°"), 
                  tick = TRUE, cex = 0.6, tcl.text = 0.2)
    )
}
```
We can also plot for each line count individually:

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/densities/"

file_name = paste0(path_name, "raw_angles.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# setting up a plot grid
par(mfrow = c(2,3))

# plotting the density estimate for all angles for all macroareas
for (i in 1:6) {

  # setting a transparency level for the curves
  alpha = 0.7
  
  # creating a subset with all angles
  angle_set <- angle_data %>% filter(macroarea == macroarea_idx[i]) %>% select(angle, line_count)
  
  # converting the angles to class circular
  angle_set$angle <- as.circular( angle_set$angle, types = "angle", 
                              template = "none", modulo = "asis", 
                              units="radians", zero = 0, 
                              rotation = c("counter", "clock") )
         
  # setting up plotting window
  par(mar = c(2, 2, 2, 2))
  
  # estimating circle density for a single area and a single line count
  density_data <- density.circular(angle_set$angle[angle_set$line_count == 1], bw = 20*5)
  
  # plotting the density on a circle
  plot(density_data, 
       col = col.alpha(1, alpha = alpha), 
       lwd = 1, ylim = c(-2.4,1.1), xlim = c(-0.5,2.4),
       axes = FALSE, main = "",
       cex.main = 0.7, ylab = "")
  title(main = paste(macroarea_idx[i]), adj = 0.1)
  
  # adding the curve of another line count
  for (i in 2:6) {
  
    density_data <- density.circular(angle_set$angle[angle_set$line_count == i], bw = 20*5)
    
    lines(density_data, col = col.alpha(i, alpha = alpha), lwd = 1)
    
  }

}

legend("bottomright", legend = paste("Line count = ", 1:6), 
       col = c(1:6), lwd = 1, bty = "n", cex = 0.7)

dev.off()
```

```{r}
# setting up a plot grid
par(mfrow = c(2,3))

# plotting the density estimate for all angles for all macroareas
for (i in 1:6){
  
  angle_set <- angle_data %>% filter(macroarea == macroarea_idx[i], line_count == 1) %>% select(angle)

  angle_set <- as.circular( angle_set$angle, types = "angle", 
                            template = "none", modulo = "asis", 
                            units="radians", zero = 0, 
                            rotation = c("counter", "clock") )
         
  # estimating circle density
  density_data <- density.circular(angle_set, bw = 20*5)
  
  # plotting the density on a circle
  par(mar = c(2, 2, 2, 2))
  
  plot(density_data, col = "black", 
       lwd = 1, ylim = c(-2.3,1.3), xlim = c(-1,3),
       axes = FALSE, main = "",
       cex.main = 0.7, ylab = "")
  title(main = paste(macroarea_idx[i]), adj = 0.1)
  
  # adding axis ticks and labels
  suppressWarnings(
    axis.circular(at = c(0, pi/2, pi, 3*pi/2), 
                  labels = c("0°", "90°", "180°", "270°"), 
                  tick = TRUE, cex = 0.6, tcl.text = 0.2)
    )
}
```


## 5.2 Plotting random samples of line drawings with all features displayed 

Constructing a filter to isolate distinct patterns:

```{r}
# creating color mapping

# Get the default palette colors (base R typically uses 8 colors)
color_palette <- palette()

# Map the sorted macroareas to the default colors (only using as many as needed)
color_map <- setNames(color_palette[2:7], levels(feature_data_set$macroarea))
```


```{r}
# setting up parameters
lc = 3
h = range(0.9, 1)
ic = 0
ls = range(0,1)

iteration = 8

# filtering
drawing_subset <- feature_data_set %>% 
  filter(line_count == lc,
         between(cosine_similarity_h, h[1], h[2]),
         intersection_count == ic
         , between(abs_avg_between_line_cosine_sim, ls[1], ls[2])
         )

# print the length of the subset
set_size = nrow(drawing_subset)
distribution = table(drawing_subset$macroarea)
distribution
```

```{r}
# setting seed
random_seed <- 2025
set.seed(random_seed)

# extracting n random drawings from the subset
n <-  9
ID <- drawing_subset[sample(nrow(drawing_subset), size = n), ]

# fixing aspect ratio and setting up a grid
par(pty="s", mfrow=c(2,5), mar = c(4, 2, 1, 1))

# plotting drawings with computations for all features 
for (i in 1:n) {
  
  ID_p <- ID$participant.label[i]
               
  features <- drawing_subset %>% filter(participant.label == ID_p, line_count == lc)
  
  drawing <- angle_data %>% filter(participant.label == ID_p, line_count == lc)
  
  intersections <- find_intersections(drawing)
  
  # plotting the lines
  plot(st_geometry(intersections[1]$lines_sf), col = color_map[drawing$macroarea], lwd = 2, xlim = c(0, 400), ylim = c(0, 400),
       #main = paste(unique(features$line_count), "line drawing by participant", unique(features$participant.label)),
       sub = paste("intersection count = ", features$intersection_count,
                   "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
                   "\nline similarity = ", round(features$abs_avg_between_line_cosine_sim, 3),
                   "\n macroarea = ", unique(drawing$macroarea)),
       cex.sub = 0.8
       )
    
  # plotting the intersection if it exists
  intersection_coords <- st_coordinates(intersections[2]$intersection_points)
  points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.7), pch = 19, cex = 0.8)
    
  # creating legend  
  
  # plotting the 'canvas' limits  
  box()
}

# adding a main title
mtext(paste("9 random drawings from a filtered subset (n =", nrow(drawing_subset),") ;", "lc =", lc, "; h = [", paste0(h[1],",",h[2]), "] ; ic =", ic, "; ls = [", paste0(ls[1],",",ls[2]), "]"), 
      outer = TRUE, cex = 0.7, line = -2)

#### saving

# finding dimensions
plot_dims <- dev.size("in")

plot_width_inch <- plot_dims[1]  
plot_height_inch <- plot_dims[2] 

# setting dpi
dpi <- 300

# Convert dimensions from inches to pixels
plot_width_pixels <- plot_width_inch * dpi
plot_height_pixels <- plot_height_inch * dpi

# plot distribution
plot(distribution, col = unique(color_map),
     cex.axis = 0.7, las = 2)
```
```{r}
# setting up file details
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/drawing_samples/"

plot_title = paste0("iteration_", iteration, "_seed_", random_seed, "_lc_", lc, "_h_", paste0(h[1],"_",h[2]), "_ic_", ic, "_ls_", paste0(ls[1],"_",ls[2]))

file_extension = ".tiff"

file_name = paste0(path_name, plot_title, file_extension)
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# setting seed
random_seed <- 2025
set.seed(random_seed)

# extracting n random drawings from the subset
n <-  9
ID <- drawing_subset[sample(nrow(drawing_subset), size = n), ]

# fixing aspect ratio and setting up a grid
par(pty="s", mfrow=c(2,5), mar = c(4, 2, 1, 1))

# plotting drawings with computations for all features 
for (i in 1:n) {
  
  ID_p <- ID$participant.label[i]
               
  features <- drawing_subset %>% filter(participant.label == ID_p, line_count == lc)
  
  drawing <- angle_data %>% filter(participant.label == ID_p, line_count == lc)
  
  intersections <- find_intersections(drawing)
  
  # plotting the lines
  plot(st_geometry(intersections[1]$lines_sf), col = color_map[drawing$macroarea], lwd = 2, xlim = c(0, 400), ylim = c(0, 400),
       #main = paste(unique(features$line_count), "line drawing by participant", unique(features$participant.label)),
       sub = paste("intersection count = ", features$intersection_count,
                   "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
                   "\nline similarity = ", round(features$abs_avg_between_line_cosine_sim, 3),
                   "\n macroarea = ", unique(drawing$macroarea)),
       cex.sub = 0.8
       )
    
  # plotting the intersection if it exists
  intersection_coords <- st_coordinates(intersections[2]$intersection_points)
  points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.7), pch = 19, cex = 0.8)
    
  # creating legend  
  
  # plotting the 'canvas' limits  
  box()
}

# adding a main title
mtext(paste("9 random drawings from a filtered subset (n =", nrow(drawing_subset),") ;", "lc =", lc, "; h = [", paste0(h[1],",",h[2]), "] ; ic =", ic, "; ls = [", paste0(ls[1],",",ls[2]), "]"), 
      outer = TRUE, cex = 0.7, line = -2)

#### saving

# finding dimensions
plot_dims <- dev.size("in")

plot_width_inch <- plot_dims[1]  
plot_height_inch <- plot_dims[2] 

# setting dpi
dpi <- 300

# Convert dimensions from inches to pixels
plot_width_pixels <- plot_width_inch * dpi
plot_height_pixels <- plot_height_inch * dpi

# plot distribution
plot(distribution, col = unique(color_map),
     cex.axis = 0.7, las = 2)

dev.off()
```

Doing the same thing but with random parameters

```{r}
drawing_subset
```


```{r}
# setting up parameters
random_seed <- 3000
set.seed(random_seed)
drawing_subset <- feature_data_set
distribution = table(drawing_subset$macroarea)
it = 11
n <-  9
ID <- drawing_subset[sample(nrow(drawing_subset), size = n), ]

# setting up file details
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/drawing_samples/"
plot_title = paste0("random_sample_", "iteration_", iteration, "_seed_", random_seed)
file_extension = ".tiff"
file_name = paste0(path_name, plot_title, file_extension)
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# fixing aspect ratio and setting up a grid
par(pty="s", mfrow=c(2,5), mar = c(4, 2, 1, 1))

# plotting drawings with computations for all features 
for (i in 1:n) {
  
  lc <- sample(1:6,1) # random line counts
  
  ID_p <- ID$participant.label[i]
               
  features <- drawing_subset %>% filter(participant.label == ID_p, line_count == lc)
  
  drawing <- angle_data %>% filter(participant.label == ID_p, line_count == lc)
  
  intersections <- find_intersections(drawing)
  
  # plotting the lines
  plot(st_geometry(intersections[1]$lines_sf), col = color_map[drawing$macroarea], lwd = 2, xlim = c(0, 400), ylim = c(0, 400),
       #main = paste(unique(features$line_count), "line drawing by participant", unique(features$participant.label)),
       sub = paste("intersection count = ", features$intersection_count,
                   "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
                   "\nline similarity = ", round(features$abs_avg_between_line_cosine_sim, 3),
                   "\n macroarea = ", unique(drawing$macroarea)),
       cex.sub = 0.8
       )
    
  # plotting the intersection if it exists
  intersection_coords <- st_coordinates(intersections[2]$intersection_points)
  points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.7), pch = 19, cex = 0.8)
    
  # creating legend  
  
  # plotting the 'canvas' limits  
  box()
}

# adding a main title
mtext(paste0("9 random drawings from the entire set (n = ", nrow(drawing_subset), ")"), 
      outer = TRUE, cex = 0.7, line = -2)

#### saving

# finding dimensions
plot_dims <- dev.size("in")

plot_width_inch <- plot_dims[1]  
plot_height_inch <- plot_dims[2] 

# setting dpi
dpi <- 300

# Convert dimensions from inches to pixels
plot_width_pixels <- plot_width_inch * dpi
plot_height_pixels <- plot_height_inch * dpi

# plot distribution
plot(distribution, col = unique(color_map),
     cex.axis = 0.7, las = 2)

dev.off()
```



Sampling random drawings, only filtered by line count:

```{r}
# setting up parameters
lc = 4
h = range(0,1)
ic = 9
ls = range(0,1)

iteration = 2

# filtering
drawing_subset <- feature_data_set %>% filter(line_count == lc
                                              #between(cosine_similarity_h, h[1], h[2]),
                                              #intersection_count > ic,
                                              #between(abs_avg_between_line_cosine_sim, ls[1], ls[2])
                                              )
# print the length of the subset
nrow(drawing_subset)
```

```{r}
# extracting n random drawings from the subset
it = 5
n <-  10
ID <- drawing_subset[sample(nrow(drawing_subset), size = n), ]

# fixing aspect ratio and setting up a grid
par(pty="s", mfrow=c(2,5), mar = c(4, 1, 1, 1))

# plotting drawings with computations for all features 
for (i in 1:n) {
  
  ID_p <- ID$participant.label[i]
  
  lc = sample(1:6,1)
               
  features <- drawing_subset %>% filter(participant.label == ID_p, line_count == lc)
  
  drawing <- angle_data %>% filter(participant.label == ID_p, line_count == lc)
  
  intersections <- find_intersections(drawing)

  # plotting the lines
  plot(st_geometry(intersections[1]$lines_sf), col = "blue", lwd = 2, xlim = c(0, 400), ylim = c(0, 400),
       #main = paste(unique(features$line_count), "line drawing by participant", unique(features$participant.label)),
       sub = paste("intersection count = ", features$intersection_count,
                   "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
                   "\nline similarity = ", round(features$abs_avg_between_line_cosine_sim, 3)),
       cex.sub = 0.8
       )
    
  # plotting the intersection if it exists
  # intersection_coords <- st_coordinates(intersections[2]$intersection_points)
  # points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 1.5)
    
  # creating legend  
  #legend("topright", legend = "Intersection(s)", col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 0.8)
  
  # plotting the 'canvas' limits  
  box()
}

# title
mtext(paste("10 random drawings (n =", nrow(drawing_subset),") ;", "lc =", lc), 
      outer = TRUE, cex = 0.8, line = -2)

# finding dimensions
plot_dims <- dev.size("in")

plot_width_inch <- plot_dims[1]  
plot_height_inch <- plot_dims[2] 

# setting dpi
dpi <- 300

# Convert dimensions from inches to pixels
plot_width_pixels <- plot_width_inch * dpi
plot_height_pixels <- plot_height_inch * dpi

## saving the plot

# generating title and path
plot_title = paste0(it, "random_","seed_", random_seed, "_lc_", lc)

plot_path = "/Users/christianstenbro/AU/BSc/Figures and visualisations/drawing_samples/"

# saving plot
png(paste0(plot_path, plot_title, ".png"), width = plot_width_pixels, height = plot_height_pixels)

# plotting

  # fixing aspect ratio and setting up a grid
  par(pty="s", mfrow=c(2,5), mar = c(5, 1, 1, 1))
  
  # plotting drawings with computations for all features 
  for (i in 1:n) {
    
    ID_p <- ID$participant.label[i]
          
    lc = sample(1:6,1)
           
    features <- drawing_subset %>% filter(participant.label == ID_p, line_count == lc)
    
    drawing <- angle_data %>% filter(participant.label == ID_p, line_count == lc)
    
    intersections <- find_intersections(drawing)
  
    # plotting the lines
    plot(st_geometry(intersections[1]$lines_sf), col = "blue", lwd = 6, xlim = c(0, 400), ylim = c(0, 400),
         #main = paste(unique(features$line_count), "line drawing by participant", unique(features$participant.label)),
         # sub = paste("intersection count = ", features$intersection_count,
         #             "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
         #             "\nline similarity = ", round(features$abs_avg_between_line_cosine_sim, 3)),
         )
    
    mtext(paste("intersection count = ", features$intersection_count,
                     "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
                     "\nline similarity = ", round(features$abs_avg_between_line_cosine_sim, 3)), 
          side = 1, line = 7, cex = 1.6)
      
    # plotting the intersection if it exists
    # intersection_coords <- st_coordinates(intersections[2]$intersection_points)
    # points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 4)
      
    # creating legend  
    #legend("topright", legend = "Intersection(s)", col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 0.8)
    
    # plotting the 'canvas' limits  
    box()
  }

mtext(paste("10 random drawings (n =", nrow(drawing_subset),") ;", "lc =", lc), 
      outer = TRUE, cex = 2, line = -4)
  
dev.off()
```

```{r}
# plotting drawings with computations for all features 

for (i in 1:40) {
  
  drawing <- angle_data %>% filter(participant.label == participant_ids[i], line_count == 2)
  features <- feature_data_set %>% filter(participant.label == participant_ids[i], line_count == 2)
  intersections <- find_intersections(drawing)
  ID <- unique(drawing$participant.label)
    
  # plotting the lines
  plot(st_geometry(intersections[1]$lines_sf), col = "blue", lwd = 2,
       main = paste(unique(features$line_count), "line drawing by participant", unique(features$participant.label)),
       sub = paste("intersection count = ", features$intersection_count,
                   "\nmean horizontality = ", round(features$cosine_similarity_h, 3),
                   "\nbetween line abs. cosine similarity = ", round(features$abs_avg_between_line_cosine_sim, 3))
       )
    
  # plotting the intersection if it exists
  if (features$intersection_count < 0){
    intersection_coords <- st_coordinates(intersections[2]$intersection_points)
    points(intersection_coords[,1], intersection_coords[,2],col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 1.5)
    legend("topright", legend = "Intersection(s)", col = col.alpha("orange", alpha = 0.8), pch = 19, cex = 0.8)
  }
  
}
```


## 5.3 Plotting distributions of the different features

### 5.3.1 Horizontality plots

Decomposed:

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/densities/"

file_name = paste0(path_name, "horizontality.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)

alpha = 0.7

par(mfrow = c(2,3), mar = c(4, 2, 2, 2))

# first, we loop through the line count variable

for (i in 1:6) {
  
  subset <- feature_data_set %>% filter(line_count == i)
  
  # creates the plot with a single
  plot(density(subset[subset$macroarea == macroarea_idx[1], 'cosine_similarity_h'], bw = "SJ", adjust = 3, from = 0, to = 1), 
       ylim = c(0,6), 
       col = col.alpha(1, alpha), main = "", xlab = "")
  title(main = paste("line count =",i), cex.main = 1, line = 0.3)
  
  for (j in 2:6) {
    
    lines(density(subset[subset$macroarea == macroarea_idx[j], 'cosine_similarity_h'], bw = "SJ", adjust = 3, from = 0, to = 1), 
          col = col.alpha(j, alpha))
  }
  
}

# legend("center", legend = macroarea_idx[1:6], 
#        col = c(1:6), lwd = 2, bty = "n", cex = 1)

#mtext("Horizontality for different line counts", outer = TRUE, cex = 1, line = -2)

dev.off()
```

Aggregated:

```{r}
par(mfrow=c(2,3), mar = c(4, 2, 2, 2))

for (i in 1:6) {
  sub <- feature_data_set %>% filter(line_count == i) %>% select(cosine_similarity_h) 
  plot(density(sub$cosine_similarity_h, bw = "SJ", adjust = 4), main = "", ylim = c(0,11))
  title(main = paste(i, " lines"), cex.main = 0.8, line = 0.3)
}
#mtext("Horizontality for different line counts", outer = TRUE, cex = 1, line = -2)
```

### 5.3.2 Line similarity plots

Aggregated:

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/densities/"

file_name = paste0(path_name, "similarity.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)

par(mfrow=c(2,3), mar = c(4, 2, 2, 2))

for (i in 2:6) {
  sub <- consine_similarity_drawing_level %>% filter(line_count == i) %>% select(cosine_similarity_mean) 
  dens(sub$cosine_similarity_mean)
  title(main = paste(i, " lines"), cex.main = 0.8, line = 0.3)
}
#mtext("Between line cosine similarity for different line counts", outer = TRUE, cex = 1, line = -2)¨

dev.off()
```

All macro areas for a single line count level:

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/densities/"

file_name = paste0(path_name, "similarity_5_lines.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)


# removing NAs
subset <- feature_data_set %>% filter(abs_avg_between_line_cosine_sim != "NA")

par(mfrow=c(2,3), mar = c(4, 2, 2, 2))

# first, select a line count subset

lc = 5

for (j in 1:6) {

  subset <- feature_data_set %>% filter(line_count == lc)
  
  # create a plot for the first line

  plot(density(subset[subset$macroarea == macroarea_idx[j], 'abs_avg_between_line_cosine_sim'], bw = "SJ", adjust = 3, from = 0, to = 1), 
       col = j, main = "", xlab = "")
  
  title(main = macroarea_idx[j], cex.main = 1, line = 0.3)
  
  # then add the lines for the other macro_areas
  
}

dev.off()
```

Unused stuff:

```{r}
# removing NAs
subset <- feature_data_set %>% filter(abs_avg_between_line_cosine_sim != "NA")

# first, select a line count subset

for (i in 1:6) {

  subset <- feature_data_set %>% filter(macroarea == macroarea_idx[i])
  
  # create a plot for the first line

  plot(density(subset[subset$line_count == 2, 'abs_avg_between_line_cosine_sim']), 
       col = col.alpha(1, alpha), main = "", xlab = "", ylim = c(0,100))
  
  # then add the lines for the other macro_areas
  
  for (j in 2:6) {
    
    lines(density(subset[subset$line_count == j, 'abs_avg_between_line_cosine_sim']), 
          col = col.alpha(j, alpha))
    
  }

    title(main = paste("area =",i), cex.main = 1, line = 0.3)
  
}


```

```{r}
# removing NAs
subset <- feature_data_set %>% filter(abs_avg_between_line_cosine_sim != "NA")

par(mfrow=c(2,3), mar = c(4, 2, 2, 2))

# first, select a line count subset

for (i in 2:6) {

  subset <- feature_data_set %>% filter(line_count == i)
  
  # create a plot for the first line

  plot(density(subset[subset$macroarea == macroarea_idx[1], 'abs_avg_between_line_cosine_sim'], bw = "SJ", adjust = 1, from = 0, to = 1), 
       col = col.alpha(1, alpha), main = "", xlab = "", ylim=c(0,1000))
  
  title(main = paste("line count =",i), cex.main = 1, line = 0.3)
  
  # then add the lines for the other macro_areas
  
  for (j in 2:6) {
    
    lines(density(subset[subset$macroarea == macroarea_idx[j], 'abs_avg_between_line_cosine_sim'], bw = "SJ", adjust = 1, from = 0, to = 1), 
          col = col.alpha(j, alpha))
    
  }
  
}

#legend("center", legend = macroarea_idx[1:6], col = c(1:6), lwd = 2, bty = "n", cex = 1)

```

### 5.3.3 Intersection plots

```{r}
for (i in 2:6) {
  
  subset <- feature_data_set %>% filter(line_count == i)
  
  plot <- ggplot(data = subset, aes(x=intersection_count, fill=macroarea)) + 
    geom_bar(alpha=1, position="dodge", show.legend = FALSE) +
    theme_minimal() +
    labs(title = paste("Line count =", i)) +
    scale_x_continuous(breaks = seq(0, 15, by = 1))
  
  print(plot)
}

```

# 6 Fitting statistical models

## 6.1 Modelling Intersections

The first model I will fit is a poisson distribution of the intersection count, taking an interaction between the (ordered categorical?) line count and the (categorical) macro area.

The variables will be defined as:

  I = intersection count
  L = line count
  M = macro area

Formally, the model can be specified as:

$$I \sim Poisson(\lambda_i)$$
$$\log{\lambda_i} = 0 + \beta_L L_i + \beta_M[M_i] + \beta_{LM}[M_i] \cdot L_i $$
The intercept is here forced to 0 to ease the interpretation of the coefficients for the different levels in the categorical predictors: The coefficients will correspond to the mean of log lambda for each category.

Before fitting the model, I will do prior predictive checks (based on McElreath, 2020, ch. 11). I will use the same uninformative prior for all three coefficients: A gaussian that allows for moderate slopes in both positive and negative directions:

$$ \beta \ \text{priors} \sim N(0,0.5)$$
To see the effect of this prior, I will sample coefficient values from the above prior distribution, simulate different categorical levels, and take the exponential of the product of the coefficients and different levels to estimate the prior prediction on the outcome (non-log) scale:

```{r}
# setting up simulation
N = 1000
b <- rnorm(N, 0 , 0.5 )
lambda = exp(b)

# setting up plotting window
par(mfrow=c(1, 2))

# plotting beta values and the effect on lambda on the outcome scale
plot(x = b, y = lambda, main = "(a) sampled beta coefficients \nand their effect on lambda",
     cex.main = 0.8, col = col.alpha(rangi2, 0.3))
grid()
abline(h = mean(lambda), lty = 2 , lwd = 1)

# plotting the distribution of lambda
dens(lambda, main = "(b) distribution of differences lambda",
     cex.main = 0.8)
abline(v = mean(lambda), lty = 2 , lwd = 1)
```

Comment on the plot:

Considering that this is the expected change in lambda (both the mean, or expected value, and the variance of the Poisson distribution) for a single change in category, the possible values for beta cover a broad range. It is unlikely that changing macro area or line count would affect the average intersection count with more than a few units (even this would be an unexpectedly large effect).

As a note, it is important to consider that the line count is an ordered categorical variable. There are three ways to deal with this: One is to code it as a categorical variable without taking the order into account; another is to code it as a continuous variable (which adds the assumption that the levels are equidistant, which they arguably are in this case); a third is to code the variable as an ordered categorical variable (for example following the approach in McElreath, 2020, ch. 12).

As a first try, I will code it as a continuous variable, as I believe it is sound to assume that the levels are equidistant (the distance between 1 line and 2 lines are the same as that between 2 and 3 lines, etc).

Notice that the beta coefficients will still be interpretable in the same way; beta tells us the expected difference in log lambda for a unit change in the line count variable.

Now to format the data and specify the model in ULAM:

```{r}
# checking the factor levels
levels(feature_data_set$macroarea)

# renaming data
d <- feature_data_set
```

```{r}
# setting up a data list for ULAM
# dat <- list(
#   I = d$intersection_count,
#   L = d$line_count,
#   M = as.integer(d$macroarea),
#   P = as.integer(factor(d$participant.label))
#   )
# 
# # approximating posterior
# ulam_m1.4 <- ulam(
#   alist(
#     I ~ dpois( lambda ),
#     log(lambda) <- 0 + b_L*L + b_M[M] + b_LM[M]*L + a[P],
#     b_L ~ dnorm(0,0.5),
#     b_M[M] ~ dnorm(0,0.5),
#     b_LM[M] ~ dnorm(0,0.5),
#     a[P] ~ dnorm(0,0.5)
#   ), data = dat , chains=4 , log_lik = TRUE, cmdstan = TRUE, cores = 4
# )
```

```{r}
# # assessing the model
# precis(ulam_m1.4, depth = 2)
# 
# # extracting posterior and coefficients
# post <- extract.samples( ulam_m1.4 )
# 
# # printing the factor levels
# levels(feature_data_set$macroarea)
```

Trying to fit the same model in brms:

```{r}
# setting up a data frame; remove centering (doesn't make sense for line count; makes it harder to interpret)
dat <- data.frame(
  I = d$intersection_count,
  L = d$line_count,
  M = d$macroarea,
  P = factor(as.integer(factor(d$participant.label)))
)

# fitting model
intersection_model_5 <- brms::brm(
  formula = I ~ 0 + M + L + L:M + (1|P),
  data = dat,
  family = poisson,
  chains = 4, iter = 2000, warmup = 1000, 
  cores = 4, seed = 2025,
  file = "intersection_model_5"
)

summary(intersection_model_5)
```

```{r}
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"

file_name = paste0(path_name, "intersection_coef_table.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# plotting the coefficients as a forest plot
posterior <- as_draws_df(intersection_model_5)

# Plot intervals for all fixed effects
mcmc_intervals(posterior, regex_pars = "^b_")  # Plot for all fixed effects

dev.off()
```


<!-- # ```{r} -->
<!-- # # plotting the posteriors -->
<!-- # dens(post$b_L) -->
<!-- # dens(post$b_LM) -->
<!-- #  -->
<!-- # # plotting the estimated coefficients for the interaction term -->
<!-- # par(mfrow=c(2,3)) -->
<!-- #  -->
<!-- # for (i in 1:6) { -->
<!-- #   dens(post$b_LM[,i], main = paste(levels(intersection_prolific_geography$macroarea)[i]), cex.main = 0.5) -->
<!-- #   abline(v = median(post$b_LM[,i])) -->
<!-- # } -->
<!-- #  -->
<!-- # par(mfrow=c(1,1)) -->
<!-- #  -->
<!-- # # plotting the coefficients as box plots -->
<!-- # boxplot_data <- rbind( -->
<!-- # data_frame(group = rep(1,2000), lambda = as.vector(post$b_LM[,1])), -->
<!-- # data_frame(group = rep(2,2000), lambda = as.vector(post$b_LM[,2])), -->
<!-- # data_frame(group = rep(3,2000), lambda = as.vector(post$b_LM[,3])), -->
<!-- # data_frame(group = rep(4,2000), lambda = as.vector(post$b_LM[,4])), -->
<!-- # data_frame(group = rep(5,2000), lambda = as.vector(post$b_LM[,5])), -->
<!-- # data_frame(group = rep(6,2000), lambda = as.vector(post$b_LM[,6]))) -->
<!-- #  -->
<!-- # path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/" -->
<!-- # file_name = paste0(path_name, "intersection_b_LM.tiff") -->
<!-- # tiff(file_name, units="in", width=7.29, height=4.51, res=500) -->
<!-- #  -->
<!-- # boxplot(boxplot_data$lambda ~ boxplot_data$group, ylab = "b_LM", xlab = "index", col = c(2,3,4,5,6,7)) -->
<!-- # #legend("bottomright", legend = c("Africa","Australia","Eurasia","North America","Papunesia","South America"), col = c(2,3,4,5,6,7), lwd = 2, bty = "n", cex = 0.6) -->
<!-- #  -->
<!-- # dev.off() -->
<!-- #  -->
<!-- # boxplot(boxplot_data$lambda ~ boxplot_data$group, ylab = "b_LM", xlab = "index", col = c(2,3,4,5,6,7)) -->
<!-- # ``` -->
<!-- # ```{r} -->
<!-- # # plotting the coefficients as box plots -->
<!-- # boxplot_data <- rbind( -->
<!-- # data_frame(group = rep(1,2000), lambda = as.vector(post$b_M[,1])), -->
<!-- # data_frame(group = rep(2,2000), lambda = as.vector(post$b_M[,2])), -->
<!-- # data_frame(group = rep(3,2000), lambda = as.vector(post$b_M[,3])), -->
<!-- # data_frame(group = rep(4,2000), lambda = as.vector(post$b_M[,4])), -->
<!-- # data_frame(group = rep(5,2000), lambda = as.vector(post$b_M[,5])), -->
<!-- # data_frame(group = rep(6,2000), lambda = as.vector(post$b_M[,6]))) -->
<!-- #  -->
<!-- # path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/" -->
<!-- # file_name = paste0(path_name, "intersection_b_M.tiff") -->
<!-- # tiff(file_name, units="in", width=7.29, height=4.51, res=500) -->
<!-- #  -->
<!-- # boxplot(boxplot_data$lambda ~ boxplot_data$group, ylab = "b_M", xlab = "index", col = c(2,3,4,5,6,7)) -->
<!-- # legend("bottomright", legend = c("Africa","Australia","Eurasia","North America","Papunesia","South America"), col = c(2,3,4,5,6,7), lwd = 2, bty = "n", cex = 0.6) -->
<!-- #  -->
<!-- # dev.off() -->
<!-- #  -->
<!-- # boxplot(boxplot_data$lambda ~ boxplot_data$group, ylab = "b_M", xlab = "index", col = c(2,3,4,5,6,7)) -->
<!-- # legend("bottomright", legend = c("Africa","Australia","Eurasia","North America","Papunesia","South America"), col = c(2,3,4,5,6,7), lwd = 2, bty = "n", cex = 0.6) -->
<!-- # ``` -->
<!-- # ```{r} -->
<!-- # path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/" -->
<!-- # file_name = paste0(path_name, "intersection_b_L.tiff") -->
<!-- # tiff(file_name, units="in", width=7.29, height=4.51, res=500) -->
<!-- #  -->
<!-- # # plotting the line count coefficient -->
<!-- # dens(post$b_L, main = "b_L") -->
<!-- # abline(v = median(post$b_L)) -->
<!-- # abline(v = HPDI(post$b_L)[1], lty = 2) -->
<!-- # abline(v = HPDI(post$b_L)[2], lty = 2) -->
<!-- #    -->
<!-- # dev.off() -->
<!-- #  -->
<!-- # dens(post$b_L, main = "b_L") -->
<!-- # abline(v = median(post$b_L)) -->
<!-- # abline(v = HPDI(post$b_L)[1], lty = 2) -->
<!-- # abline(v = HPDI(post$b_L)[2], lty = 2) -->
<!-- # ``` -->

### 6.1.1 Posterior predictive checks

```{r}
post_check_int_a <- brms::pp_check(intersection_model_5, ndraws = 100, type = "bars")
post_check_int_b <- brms::pp_check(intersection_model_5, ndraws = 100, type = "bars_grouped", group = "M")
post_check_int_c <- brms::pp_check(intersection_model_5, ndraws = 100, type = "violin_grouped", group = "M")

post_check_int_a
post_check_int_b
post_check_int_c
```

### 6.1.2 Conditional effects

```{r}
c(levels(d$macroarea))
```

```{r}
# setting up file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"
file_name = paste0(path_name, "intersection_ce_interaction.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# Plotting the interaction
ce <- brms:::conditional_effects(intersection_model_5, effects = "L:M")
ce_plot <- plot(ce, plot = FALSE)[["L:M"]]

ce_plot +
  labs(
    title = "Intersection Model Conditional Effects: Interaction",
    y = "Expected Avg. Intersections",
    x = "Line Count"
  ) +
    theme(
      axis.text = element_text(size = 7)
    )

dev.off()

# setting up file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"
file_name = paste0(path_name, "intersection_ce_macroarea.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# Plotting the effect of macro area on its own
ce_box <- brms:::conditional_effects(intersection_model_5, effects = "M")
ce_boxplot <- plot(ce_box, plot = FALSE)[["M"]]

ce_boxplot +
  labs(
    title = "Intersection Model Conditional Effects: Macroarea",
    y = "Expected Avg. Intersections",
    x = "Macroarea") +
    theme(
      axis.text = element_text(size = 7)
    )

dev.off()
```
### 6.1.3 Bayesian R-squared

```{r}
set.seed(seed = 2025)
R2 <- rstantools::bayes_R2(intersection_model_5)
looR2 <- rstantools::loo_R2(intersection_model_5)

R2
round(looR2, 3)
```


## 6.2 Modelling Horizontality

```{r}
# setting up the data frame
dat <- data.frame(
  CS_h = feature_data_set$cosine_similarity_h * (feature_data_set$cosine_similarity_h * (nrow(feature_data_set) - 1) + 0.5) / nrow(feature_data_set), # scaling the cosine similarities so that all values x meet the following condition: 0 < x < 1
  M = factor(feature_data_set$macroarea),
  L = feature_data_set$line_count,
  P = factor(as.integer(factor(feature_data_set$participant.label))) # converting PIDs to integers
)
```

```{r}
# fitting a model with random effects
mdl_4_6_g <- brms::brm(
  bf(CS_h ~ 0 + L + M + L*M + (1|P),
     phi ~ 0 + L + M),
  data = dat,
  family = Beta(),
  chains = 4, iter = 2000, warmup = 1000, 
  cores = 4, seed = 2025,
  file = "mdl_4_6_g"
)

# checking the summary
summary(mdl_4_6_g)
```

Alternative formula:

```{r}
# # fitting a model with random effects
# mdl_4_6_g_a <- brms::brm(
#   bf(CS_h ~ 0 + L + M + L:M + (1|P),
#      phi ~ 0 + L + M),
#   data = dat,
#   family = Beta(),
#   chains = 4, iter = 2000, warmup = 1000, 
#   cores = 4, seed = 2025,
#   file = "mdl_4_6_g_a"
# )
# 
# # checking the summary
# summary(mdl_4_6_g_a)
```


```{r}
# Extract posterior draws
posterior <- as_draws_df(mdl_4_6_g)

# Plot intervals for all fixed effects
mcmc_intervals(posterior, regex_pars = "^b_")  # Plot for all fixed effects

# saving file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"

file_name = paste0(path_name, "horizontality_coef_table.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)

mcmc_intervals(posterior, regex_pars = "^b_")

dev.off()
```
### 6.2.1 Posterior predictive checks

Trying posterior predictive checks:

```{r}
pp_check_6.2.a <- brms::pp_check(mdl_4_6_g, ndraws = 100)
pp_check_6.2.a
```
This is honestly not that bad! The bimodal nature of the data is captured by the beta model, balancing the fact that the peak at 1 (indicating horizontal lines) is bigger than the peak at 0 (verticality). However, the model does not (and theoretically, cannot) take the multimodal nature of the actual distribution into account. Hence, the meaningful variation between 1 and 0 is all lost in this model.

I will make a similar plot where the regional groups are incorporated:

```{r}
pp_check_6.2.b <- brms::pp_check(mdl_4_6_g, ndraws = 100, type = "violin_grouped", group = "M")
pp_check_6.2.c <- brms::pp_check(mdl_4_6_g, ndraws = 100, type = "dens_overlay_grouped", group = "M")

pp_check_6.2.b
pp_check_6.2.c
```
It is clear (especially from plot pp_check_6.2.c) that the model fails to capture the variation in everything that's going on between the peaks. 

As such, the model can only be used to describe the differences in the relative distribution of the two peaks (horizontality and verticality), while differences in whatever is between the peaks (and there *are* clear meaningful differences based on the above plot, and the visualisations in point 5) is left undebscribed.

### 6.2.2 Conditional effects

```{r}
# Plotting the interaction
brms:::conditional_effects(mdl_4_6_g, effects = "L:M")

# Plotting the effect of macro area on its own
#conditions <- data.frame(L = c(1, 2, 3, 4, 5, 6))
brms:::conditional_effects(mdl_4_6_g, effects = "M") 


ce <- brms:::conditional_effects(mdl_4_6_g, effects = "L:M")
ce_plot <- plot(ce, plot = FALSE)[["L:M"]]

ce_plot +
  labs(
    title = "Horizontality Model Conditional Effects: Interaction",
    y = "Expected Horizontality",
    x = "Line Count"
  )

ce_box <- brms:::conditional_effects(mdl_4_6_g, effects = "M") 
ce_boxplot <- plot(ce_box, plot = FALSE)[["M"]]

ce_boxplot +
  labs(
    title = "Horizontality Model Conditional Effects: Macroarea",
    y = "Expected Horizontality",
    x = "Macroarea")
```
```{r}
# setting up file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"
file_name = paste0(path_name, "horizontality_ce_interaction.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# Plotting the interaction
ce <- brms:::conditional_effects(mdl_4_6_g, effects = "L:M")
ce_plot <- plot(ce, plot = FALSE)[["L:M"]]

ce_plot +
  labs(
    title = "Horizontality Model Conditional Effects: Interaction",
    y = "Expected Avg. Horizontality",
    x = "Line Count"
  ) +
  theme(
      axis.text = element_text(size = 7)
    )

dev.off()

# setting up file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"
file_name = paste0(path_name, "horizontality_ce_macroarea.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# Plotting the effect of macro area on its own
ce_box <- brms:::conditional_effects(mdl_4_6_g, effects = "M") 
ce_boxplot <- plot(ce_box, plot = FALSE)[["M"]]

ce_boxplot +
  labs(
    title = "Horizontality Model Conditional Effects: Macroarea",
    y = "Expected Avg. Horizontality",
    x = "Macroarea") +
    theme(
      axis.text = element_text(size = 7)
    )

dev.off()
```
### 6.2.3 Bayesian R-squared

```{r}
set.seed(seed = 2025)
R2 <- rstantools::bayes_R2(mdl_4_6_g)
looR2 <- rstantools::loo_R2(mdl_4_6_g)

R2
round(looR2, 3)
```


## 6.3 Modelling Similarity

### 6.3.1 Conceptualising model

I will use the parameterisation of the beta distribution used in McElreath (2020), ch. 12, and further described here: https://bookdown.org/content/4857/monsters-and-mixtures.html

McElreath writes the following about the parameters:

"A beta distribution has two parameters, *an average probability pbar* and *a shape parameter thetaØ. The shape parameter theta describes how spread out the distribution is. When theta = 2, every probability from zero to 1 is equally likely. As theta increases above 2, the distribution of probabilities grow more concentrated. When theta < 2, the distribution is so dispersed that extreme probabilities near zero and 1 are more likely than the mean." (McElreath, 2020, p. 371)

Trying out different parameters of a beta distribution:

```{r}
# different values for pbar with fixed theta
pbar <- seq(from = 0, to = 1, by = 1/6)
theta <- 5

par(mfrow=c(2,3))

for (i in 1:6) {
curve( dbeta2(x,pbar[i],theta) , from=0 , to=1 ,
       xlab="probability" , ylab="Density", main = paste("pbar =", round(pbar[i], 3)))
}

# different values for theta with fixed pbar 
theta <- seq(from = 0, to = 6, by = 6/6)
pbar <- 0.5

par(mfrow=c(2,3))

for (i in 1:6) {
curve( dbeta2(x,pbar,theta[i]) , from=0 , to=1 ,
       xlab="probability" , ylab="Density", main = paste("theta =", round(theta[i], 3)))
}

```

```{r}
curve( dbeta2(x,0.7, 0.8) , from=0 , to=1 ,
       xlab="probability" , ylab="Density")
```


The following visualisation from https://bookdown.org/content/4857/monsters-and-mixtures.html is also super neat. Here, the pbar value is expressed mu and the theta as kappa:

```{r}
crossing(pbar  = c(.25, .5, .75),
         theta = c(5, 15, 30)) %>% 
  expand_grid(x = seq(from = 0, to = 1, length.out = 100)) %>% 
  mutate(density = rethinking::dbeta2(x, prob = pbar, theta = theta),
         mu      = str_c("mu == ", pbar %>% str_remove(., "0")),
         kappa   = factor(str_c("kappa == ", theta), 
                          levels = c("kappa == 30", "kappa == 15", "kappa == 5"))) %>% 
  
  # plot
  ggplot(aes(x = x, y = density)) +
  geom_area(fill = canva_pal("Green fields")(4)[4]) +
  scale_x_continuous("probability space", 
                     breaks = c(0, .5, 1), labels = c("0", ".5", "1")) +
  scale_y_continuous(NULL, labels = NULL) +
  theme(axis.ticks.y = element_blank()) +
  facet_grid(kappa ~ mu, labeller = label_parsed)
```

The variables of the model are defined: 

CS = cosine similarity mean
M = macro area
L = line count
P = participant

The model is defined:

$$ CS_i \sim Beta(\bar{p}_i, \theta)$$
$$ \log \bar{p}_i = 0 + \beta_{M[i]} + \beta_L L_i + \beta_{LM[i]} L_i + \alpha_{P[i]} $$
$$ \beta_{[M, L, LM]} \sim \text{some prior} $$
$$ \alpha_P \sim \text{some prior} $$
$$ \theta \sim \text{some prior} $$
The model is working on the level of the individual drawing, meaning that it is possible to investigate potential systematic variation in the mean cosine similarity as a interactive function of the line count and the geographic region. 

I will need to decide on priors for the beta coefficients, the alpha coefficients, and the theta parameter.

### 6.3.2 Prior predictive checks

### 6.3.3 Fitting model

```{r}
dat <- data.frame(
  CS = feature_data_set$abs_avg_between_line_cosine_sim * (feature_data_set$abs_avg_between_line_cosine_sim * (nrow(feature_data_set) - 1) + 0.5) / nrow(feature_data_set),
  M = factor(feature_data_set$macroarea),
  L = feature_data_set$line_count,
  P = factor(as.integer(factor(feature_data_set$participant.label)))
)

# mdl_6_2_a <- rstanarm::stan_betareg(CS ~ 0 + L + M + M*L, data = dat, link = "logit", link.phi = "log",
#                      cores = 4, seed = 2025)

mdl_6_2_b <- brms::brm(
  bf(CS ~ 0 + L + M + L*M + (1|P),
     phi ~ 0 + L + M),
  data = dat,
  family = Beta(),
  chains = 4, iter = 2000, warmup = 1000, 
  cores = 4, seed = 2025,
  file = "mdl_6_2_b"
)

summary(mdl_6_2_b)
```

```{r}
# Extract posterior draws
posterior <- as_draws_df(mdl_6_2_b)

# Plot intervals for all fixed effects
mcmc_intervals(posterior, regex_pars = "^b_")  # Plot for all fixed effects

# saving file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"

file_name = paste0(path_name, "similarity_coef_table.tiff")

tiff(file_name, units="in", width=7.29, height=4.51, res=500)

mcmc_intervals(posterior, regex_pars = "^b_")

dev.off()
```
### 6.3.4 Posterior predictive checks

```{r}
pp_check_6.3.a <- brms::pp_check(mdl_6_2_b, ndraws = 100)
pp_check_6.3.a
```

```{r}
pp_check_6.3.b <- brms::pp_check(mdl_6_2_b, ndraws = 100, type = "violin_grouped", group = "M")
pp_check_6.3.c <- brms::pp_check(mdl_6_2_b, ndraws = 100, type = "dens_overlay_grouped", group = "M")
pp_check_6.3.d <- brms::pp_check(mdl_6_2_b, ndraws = 100, type = "ecdf_overlay_grouped", group = "M")

pp_check_6.3.b
pp_check_6.3.c
pp_check_6.3.d
```

### 6.3.5 Conditional effects

```{r}
# conditions <- brms::make_conditions(mdl_6_2_b, "M")
# 
# conditions <- data.frame(L = c(1, 2, 3, 4, 5, 6))
```


```{r}
#brms:::conditional_effects(mdl_6_2_b, effects = "L:M", conditions = conditions)

brms:::conditional_effects(mdl_6_2_b, effects = "L:M")
brms:::conditional_effects(mdl_6_2_b, effects = "M")
```
```{r}
# setting up file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"
file_name = paste0(path_name, "similarity_ce_interaction.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# Plotting the interaction
ce <- brms:::conditional_effects(mdl_6_2_b, effects = "L:M")
ce_plot <- plot(ce, plot = FALSE)[["L:M"]]

ce_plot +
  labs(
    title = "Similarity Model Conditional Effects: Interaction",
    y = "Expected Avg. Similarity",
    x = "Line Count"
  ) +
    theme(
      axis.text = element_text(size = 7)
    )

dev.off()

# setting up file
path_name = "/Users/christianstenbro/AU/BSc/Figures and visualisations/models/"
file_name = paste0(path_name, "similarity_ce_macroarea.tiff")
tiff(file_name, units="in", width=7.29, height=4.51, res=500)

# Plotting the effect of macro area on its own
ce_box <- brms:::conditional_effects(mdl_6_2_b, effects = "M")
ce_boxplot <- plot(ce_box, plot = FALSE)[["M"]]

ce_boxplot +
  labs(
    title = "Similarity Model Conditional Effects: Macroarea",
    y = "Expected Avg. Similarity",
    x = "Macroarea") +
    theme(
      axis.text = element_text(size = 7)
    )

dev.off()
```

### 6.3.6 Bayesian R-squared

```{r}
set.seed(seed = 2025)
R2 <- rstantools::bayes_R2(mdl_6_2_b)
looR2 <- rstantools::loo_R2(mdl_6_2_b)

R2
round(looR2, 3)
```

